---
title: 'Teaching: Promotion and Tenure Document'
author: "Daniel Fuller"
output:
      html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Daniel Fuller, Ph.D.  
Canada Research Chair in Population Physical Activity  
Assistant Professor  
School of Human Kinetics and Recreation   
Physical Education Building PE 2024 Memorial   
University of Newfoundland St. John’s, NL  
A1C 5S7  
Tel: (709) 864-7270    
E-mail: dfuller@mun.ca    
Web: [http://www.walkabilly.ca/](http://www.walkabilly.ca/)  

### <span style="color:#81112c">The important thing is not to stop questioning. Curiosity has its own reason for existing.</span>

#### <span style="color:#81112c">Albert Einstein</span>

***

## <span style="color:#81112c">Teaching Philosophy</span>

My primary intention as a teacher is to create a learning environment in which my students and I can learn together, can understand and critically reflect on threshold concepts in public health. I strive to evoke passion and nuance in my students’ thinking and to promote the integration of concepts and perspective from multiple disciplines. Given the ready availability of information, it is no longer sufficient for students simply to memorize concepts and definitions. The contemporary challenge for both teachers and students involves conceptual exploration and innovations that bring together ideas from multiple disciplines to deepen our understanding of the world, appreciating both complexity and ambiguity. As a teacher I attempt to collaborate with students in creating the best learning environment.
 
To accomplish my teaching and learning outcomes I combine technological innovation, inspiring in-class interactive learning and problem based learning. Technological innovations in my courses include podcasting lectures, online forums and mobile availability of course material. Technology, however, cannot be a substitute for human interaction. My class presentations encourage interactions and critical reflection with and among students, providing conceptual brainteasers for students’ reflection to conclude each class. Students need to recognize that universities are integral community members. Through problem based learning opportunities, students are challenged to engage their knowledge and understanding through reflective practice. Problem based learning allows students to explore and learn firsthand the principles of public health, theory and methods.
 
To assess progress toward my teaching and learning outcomes I draw on students’ evaluations, fellow teachers’ peer evaluations, and my students’ accomplishments in major scholarship competitions. These assessment strategies encourage continuous development of my teaching based on students’ learning. A reflexive approach to teaching and learning demands that I remain self-critical and adapt to meeting the changing needs, competencies, and hopes of my students, the fundamental purpose of my teaching practices.
 
Teaching and learning create remarkable moments in our human experience. From watching the joy of a child ride a bike for the first time to that “aha” moment when a student finally “gets” a challenging concept, such learning moments imprint themselves in our memory. For me, teaching involves that wonder. The hard work of remote and immediate preparation in teaching is transformed into the joy of these indelible learning moments. Although these moments are rare, they are transforming. I am motivated and strive to create such opportunities in each of my courses so that students can experience and prove to themselves they are more and can become more than they have previously believed.

## <span style="color:#81112c">Courses Taught</span>

| Institution | Year | Term | Course | Topic | Role |
|-------------|------|------|--------|-------|------|
| Memorial University| 2018 | Winter | HKR 3400 | Social Determinants of Health | Instructor | 
|  | 2018 | Winter | HKR 6134 | Seminar | Instructor |
|  | 2017 | Fall | HKR 6130 | Computer Applications for Physical Activity Measurement and Intervention | Instructor |
|  | 2017 | Fall | HKR 6134 | Seminar | Instructor |

### <span style="color:#81112c">6130 Computer Applications for Physical Activity Measurement and Intervention</span>

#### Course Description  **[Course outline](https://github.com/walkabilly/HKR6130_MUN/blob/master/course_outline.md)**
This course will introduce students to physical activity measurement using accelerometer devices including smartphones, smartwatches. I will also introduce students to measuring spatial location using Global Positioning Systems. The course will explore conceptual aspects of physical activity and spatial location measurement. Students will design, conduct, and analyse data for a small-scale intervention collecting accelerometer measured physical activity and GPS data. Students will learn programming in R and QGIS for spatial analysis methods.  

#### Course Learning Objectives  
1. Demonstrate an understanding of objective physical activity and spatial location measurement
2. Compare and contrast available technologies for physical activity measurement
3. Basic programming in R and QGIS
4. Design, conduct, and analyse data from a small-scale intervention using smart devices

### <span style="color:#81112c">6134 Seminar</span>

#### Course Description
This course provides students with a forum to discuss and debate research methods and skills such as manuscript and grant writting. The course is designed to provide students with both conceptual and practical course content, using a variety of formats, to enhance student learning. 
 
#### Course Learning Objectives  
By the end of the course, the student will  
1.	Discuss trends and contentious issues in research methods     
2.	Practice research presentation skills     
3.	Be exposed to academic grant and manuscript writing skills  

### <span style="color:#81112c">3400 Social Determinants of Health</span>

#### Course Description
This course provides students with a social, political, economic, environmental, and cultural perspective on health and health inequalities. A concentrated look at contemporary health issues using the social determinants of health model will equip students with critical skills necessary to consider health issues beyond physical pathologies.

#### Course Learning Objectives  
By the end of the course, the student will  
1.	Describe the theories and concepts of social determinants of health research    
2.	Present and discuss current social determinants of health issues   
3.	Develop a written argument about a social determinants of health topic    
4.	Recognize the role of culture in human kinetics and recreation   

## <span style="color:#81112c">Guest Lectures</span>

| Course | Instructor | Lecture | Year | Institution | 
|--------|------------|---------|------|-------------|
| HKR 2000 | Dr. Kevin Power | Physical Activity Epidemiology | 2018 | Memorial University | 
| HKR 2000 | Dr. Kevin Power | Population Approach to Physical Activity | 2017 | Memorial University | 

## <span style="color:#81112c">Undergraduate Student Supervision</span>

| Name | Program | Project | Term |
|------|--------|--------|------|
| Logan Slade | Human Kinetics and Recreation | MUCEP | Fall 2018 |
| Abbie Humphreys | Humanities and Social Sciences | MUCEP | Summer 2018 |

## <span style="color:#81112c">Graduate Student Supervision</span>  

| Name | Program | Project | Completion | Institution | Role | 
|------|---------|---------|------------|-------------|------| 
| Melissa Tobin | Human Kinetics and Recreation | MSc Student | Expected 2018 | Memorial University | Supervisor |  
| Bo Simango | Human Kinetics and Recreation | MSc Student | Expected 2018 | Memorial University | Supervisor |  
| Kassia Orychock | Human Kinetics and Recreation | MSc Student | Expected 2018 | Memorial University | Supervisor |  
| Kate Hosford | Public Health | MSc Student | Expected 2018 | Simon Fraser University |  Committee Member |  
| Pablo Navarro | Community Health and Humanities | PhD Student | Expected 2019 | Memorial University |  Committee Member |
| Se’era Anstruthers | Nutrition | MSc Student | Expected 2019 | University of Saskatchewan |  Committee Member |  
| Larisa Lotoski | Epidemiology | PhD Student | Expected 2018 | University of Saskatchewan | Committee Member |  
| Adriana Fonseca | Epidemiology | PhD Student | Expected 2020 |  University of Saskatchewan | Committee Member |  

## <span style="color:#81112c">Graduated Students</span>  

| Name | Program | Project | Institution | Role | 
|------|---------|---------|-------------|------| 
| Nathan Taylor | Public Health | Practicum Student | Memorial University | Practicum Supervisor | 
| Amita Goyal | HKR | MSc Student | MUN |  Reviewer |  


## <span style="color:#81112c">Post Doctoral Fellows</span>

| Name | Program  | Completion | Institution | 
|------|---------|------------|-------------| 
| Hui (Henry) Luan | Post Doctoral Fellow | 2018 | Memorial University | 

## <span style="color:#81112c">Professional Development in Teaching</span>  

April 27, 2017: Transformational Teaching and Learning Day. Centre for Innovation in Teaching and Learning, Memorial University.  

## <span style="color:#81112c">Course Evaluations</span>

I have included CEQ results for all course for which they were available. Some courses had too few responses and results were not made available. 

**Courses taught**

- HKR 3400 Winter 2018: See Appendix T_1 for evaluations
- HKR 6130 Fall 2017 and Winter 2017: See Appendix T_2 for evaluations
- HKR 6130 Fall 2017: See Appendix T_3 for evaluations 

#### <span style="color:#81112c">Course Evaluations</span>

Additonally, I have conducted my own course evaluations for HKR 3400 and HKR 6134. The data are from 13 students in HKR 3400 (out of a possible 62 students) and 18 students in HKR 6134 (our of a possible 35). The questions posted were:   
    1. The instructor used challenging questions   
    2. The instructor was willing to listen to student opinions  
    3. The instructor was actively helpful to the students  
    4. The instructor had a genuine interest in student learning  
    5. The course materials (e.g., readings, notes, in‐class exercises) facilitated learning  
    6. The general atmosphere in this course was good for learning  
    7. The instructor related to students in ways that promoted mutual respect  
    8. The instructor provided adequate opportunities for questions and discussion during class time  
    9. Students were invited to share their ideas  
    10. In this course, I felt motivated to learn  
    
Below I present only a subset of the data. However, what is presented provides a good general picture of the evaluations. 

```{r, warning=FALSE, echo = FALSE}
library(readxl)
teaching1 <- read_excel("/Users/dfuller/Dropbox/Teaching/Evaluations/MUNEvaluations.xlsx")
``` 

```{r, warning=FALSE, echo = FALSE, message=FALSE}
library(dplyr)
library(reshape2)
library(ggplot2)

teaching1$course_num <- as.factor(teaching1$course_num)
ggplot(teaching1, aes(q_challenging, group=course_num, col=course_num)) + 
  geom_density(position='dodge') + 
  xlim(1, 5) + 
  labs(colour = "Course Number") + 
  labs(title = "The instructor used challenging questions") + 
  labs(x = "Scale")

teaching1$course_num <- as.factor(teaching1$course_num)
ggplot(teaching1, aes(q_listen, group=course_num, col=course_num)) + 
  geom_density(position='dodge') + 
  xlim(1, 5) + 
  labs(colour = "Course Number") + 
  labs(title = "The instructor was willing to listen to student opinions") + 
  labs(x = "Scale")

teaching1$course_num <- as.factor(teaching1$course_num)
ggplot(teaching1, aes(q_helpful, group=course_num, col=course_num)) + 
  geom_density(position='dodge') + 
  xlim(1, 5) + 
  labs(colour = "Course Number") + 
  labs(title = "The instructor was actively helpful to the students") + 
  labs(x = "Scale")

teaching1$course_num <- as.factor(teaching1$course_num)
ggplot(teaching1, aes(q_atmosphere_good, group=course_num, col=course_num)) + 
  geom_density(position='dodge') + 
  xlim(1, 5) + 
  labs(colour = "Course Number") + 
  labs(title = "The general atmosphere in this course was good for learning") + 
  labs(x = "Scale")

teaching1$course_num <- as.factor(teaching1$course_num)
ggplot(teaching1, aes(q_share_ideas, group=course_num, col=course_num)) + 
  geom_density(position='dodge') + 
  xlim(1, 5) + 
  labs(colour = "Course Number") + 
  labs(title = "Students were invited to share their ideas") + 
  labs(x = "Scale")
``` 

### <span style="color:#81112c">Comments from HKR 3400 Winter 2018</span>

Fuller, Daniel - HKR 3400 (crn: 88389)  
Q 14 = If you had to select the best aspects of this course, what would they be?  
Q 15 = What aspects of this course could be improved and how could they be improved?  
Q 26 = Instructor requested feedback (if applicable)  

| Q  |  Comment |
|----|---------------------------------------------------------------------------|
|14 |  Good instructor always willing to help when needed, gives good feedback and is clear|
|14 |  the feedback of article draft to then expand for final paper! Final paper so much better after feedback - opens eyes to new ideas and perspectives when feedback received |
|14 |  I enjoyed the lightning talks and listening to different things that interest individuals |
|14 |  Dr. Fuller had course notes well written, organized, and easily accessible on D2L. His grading was fair and he provided appropriate feedback. He was willing to meet with students to discuss their final paper and gave helpful advice. |
|14 |  great instructing |
|15 |  organization, format of exams |
|15 |  the instruction for the assignments were poorly given, a lot of confusion when knowing what was expected. The course could have been offered online with the content. |
|15 |  Too many group assignments and discussions that wasted time. I would have learned more if the professor spent the majority of class time lecturing. This course has great concepts, however I wanted to see more coming from the professor as that is how I learn best. Participation marking was easy marks but unless you are comfortable speaking in front of a class all the time then you may want to avoid it. |
|15 |  Link the book and notes more to the exams |
|15 |  Organziation and feedback provided for draft article, and provide what is expected for midterm |
|15 |  the course material could have been more detailed |
|26 |  Dr. Fuller is very approachable and is overall a nice guy. I know that he is very knowledgeable in his area and I wish he shared his insight more. |

### <span style="color:#81112c">Comments from HKR 6314 Winter 2017</span>

Fuller, Daniel - HKR 6314 (crn: 63291)  
Q 14 = If you had to select the best aspects of this course, what would they be?  
Q 15 = What aspects of this course could be improved and how could they be improved?  
Q 26 = Instructor requested feedback (if applicable)   

| Q | Comments |
|----| ---------------------------------------------------------------------------|
|14 |  Dr. Fuller's creativity and ability to create diverse seminars that link together research and it's applicability to the world as we know it. He does a great job of encouraging us to think critically and analyze every aspect of a paper (even if he encourages to tell us how bad his papers are sometimes) |
|14 |  The instructor of this course prepared helpful materials and topics in every class for students. These materials helped all students deeply think about research process and methods.|
|15 |  I think this course was perfect. I appreciated the instructor of this course. |
|15 |  This course has already undergone a huge improvement from F2016 and W2017 semesters. Keep it up!|

